A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Proposal upgrade

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their inspiration. Our focus was not on a single animal species but all of
them, using general abstraction to identify what those species have in common.

@@

From the ground up, we designed the algorithm as a cloud-native solution using
the cloud available resources to divide the processing workload, among several
computers or running the algorithm as a cloud service. The algorithm works
concurrently and asynchronously on a constantly evolving population, using
different computers (or containers) independently, theoretically eliminating
waiting times between processes.

>>>>

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their own. Our focus was not on a single animal species but all of them, using
general abstraction to identify what those species have in common.

@@

One of the main challenges when designing the algorithm was how to capture the
essence of life by reflecting a population evolution?. In our minds, it was
clear this task requires a combination of simultaneous working forces that
influences the population improvement over time. Our strategy was simple:
divide and conquer, looking into the clouds. Enter cloud-computing: previous
cloud-computing algorithms have proven successful results working in
optimization problems \cite{garcia2021event}.

We turned back to our genetic algorithms knowledge, mixed with our inspiration
and cloud computing, and designed the algorithm with the quest to divide the
processing workload among multiple computers. This strategy would also make it
possible to run our algorithm as a cloud service. Theoretically, one
consequence of the workload distribution is to obtain lower execution times.
